---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[English](README.md) | [日本語](README_JP.md)

# seq.geometric

<!-- badges: start -->
<!-- badges: end -->

`{seq.geometric}` is function to generate a sequence of equal ratios, also known as a geometric sequence.

## Installation

You can install of `{seq.geometric}` from Github with:

``` r
install.packages("remotes")
remotes::install_github("indenkun/seq.geometric")
```

## Example

```{r example}
library(seq.geometric)
```

By specifying the first term in `from`, the last term or the closest value to the last term in `to`, and the common ratio in `by.rate`, you can obtain an geometric sequence of "first term * common ratio ^ n" from "from" to the closest value to "to".

```{r}
seq_geometric(from = 1, to = 128, by.ratio = 2)
```

Returns an error if the geometric sequence does not converge with the specified argument.

```{r, error = TRUE}
seq_geometric(from = 1, to = 100, by.ratio = 0.1)
```

You can also specify the length of the sequence you want as an argument to `lenght.out`.

```{r}
seq_geometric(from = 1, to = 128, by.ratio = 2, length.out = 3)
```

## License

MIT.

## Notice

The email address listed in the DESCRIPTION is a dummy. If you have any questions, please post them on ISSUE.
